### 2022-05-26 GB_3species.Rmd
Decreasing parameters and aligning survey file with server

#decreasing populations
Pop <- init_pop_Bens(sim_init = sim, Bio = c("spp1" = 50000, "spp2" = (13000+30000)/2, "spp3" = 150000*1.2), #CHANGE
                     hab = hab[["hab"]], start_cell = list("spp1" = c(46,112),"spp2" = c(30,134),"spp3" = c(24,91)),
                     lambda = c("spp1" = 0, "spp2" = 0, "spp3" = 0), #set at 0 first, change after initial population set
                     init_move_steps = 20,
                     rec_params = list("spp1" = c("model" = "BH", "a" = 1.071946e+12, "b" = 2.296998e+12, "cv" = 0.55),
                                       "spp2" = c("model" = "BH", "a" = 389480664 , "b" = 980163673, "cv" = 0.55),
                                       "spp3" = c("model" = "BH", "a" = 497371062, "b" = 2078612769, "cv" = 0.55)), #CHANGE
                     rec_wk = list("spp1" = 9:12, "spp2" = 8:13, "spp3" = 11:14),
                     spwn_wk = list("spp1" = 9:12, "spp2" = 8:13, "spp3" = 11:14  ), 
                     M = c("spp1" = .2064+.358, "spp2" = .2728+.511, "spp3" = .334+.45), #NEED F
                     K = c("spp1" = -log((1+exp(-.2295))^(1/52)-1), "spp2" = -log((1+exp(-.16))^(1/52)-1), "spp3" = -log((1+exp(-.2465))^(1/52)-1)),
                     #  K = c("spp1" = .2295, "spp2" = .16, "spp3" = .2465),
                     Weight_PreRecruit = (c("spp1" = .13/.39, "spp2" = .39/2.95, "spp3" = .19/1.12)),
                     Weight_Adult = (c("spp1" = 1, "spp2" = 1, "spp3" = 1)),
                     nz = nonzero_idx)

@@

    #load increase temp data from Mars
    load("/net/home5/blevy/Bens_R_Projects/READ-PDB-blevy2-MFS2/Results/GB_3species_IncPop_IncTemp_environment.RData")

@@

    start_time <- Sys.time() # record start time
    p<-profmem::profmem({

    res<- run_sim(sim_init = sim,
                  pop_init = Pop,
                  move_cov = moveCov,
                  fleets_init = fleets,
                  hab_init = hab,
                  save_pop_bio = TRUE,
                  survey = NULL, #surv_random, will try to survey after simulation
                  closure = NULL,
                  InParallel = TRUE,
                  nz = nonzero_idx)  #does it runin parallel? Doesnt seem like it
    })
    end_time <- Sys.time() # record end time
    tot_time <- end_time - start_time # calculate duration of lrren() example

@@

nCoresToUse <- 4

@@

#save results
save.image("/net/home5/blevy/Bens_R_Projects/READ-PDB-blevy2-MFS2/Results/GB_3species_ConPop_IncTemp_RESULTS.RData")

>>>>

#decreasing populations
Pop <- init_pop_Bens(sim_init = sim, Bio = c("spp1" = 50000, "spp2" = (13000+30000)/2, "spp3" = 150000*1.2), #CHANGE
                     hab = hab[["hab"]], start_cell = list("spp1" = c(46,112),"spp2" = c(30,134),"spp3" = c(24,91)),
                     lambda = c("spp1" = 0, "spp2" = 0, "spp3" = 0), #set at 0 first, change after initial population set
                     init_move_steps = 20,
                     rec_params = list("spp1" = c("model" = "BH", "a" = 1.071946e+12, "b" = 2.296998e+12, "cv" = 0.55),
                                       "spp2" = c("model" = "BH", "a" = 389480664 , "b" = 980163673, "cv" = 0.55),
                                       "spp3" = c("model" = "BH", "a" = 497371062, "b" = 2078612769, "cv" = 0.55)), #CHANGE
                     rec_wk = list("spp1" = 9:12, "spp2" = 8:13, "spp3" = 11:14),
                     spwn_wk = list("spp1" = 9:12, "spp2" = 8:13, "spp3" = 11:14  ), 
                     M = c("spp1" = .2064+.358+.2, "spp2" = .2728+.35, "spp3" = .334), #NEED F
                     K = c("spp1" = -log((1+exp(-.2295))^(1/52)-1), "spp2" = -log((1+exp(-.16))^(1/52)-1), "spp3" = -log((1+exp(-.2465))^(1/52)-1)),
                     #  K = c("spp1" = .2295, "spp2" = .16, "spp3" = .2465),
                     Weight_PreRecruit = (c("spp1" = .13/.39, "spp2" = .39/2.95, "spp3" = .19/1.12)),
                     Weight_Adult = (c("spp1" = 1, "spp2" = 1, "spp3" = 1)),
                     nz = nonzero_idx)

@@

    #load increase temp data from Mars
    load("/net/home5/blevy/Bens_R_Projects/READ-PDB-blevy2-MFS2/Results/GB_3species_DecPop_IncTemp_environment.RData")

@@

    start_time <- Sys.time() # record start time
   # p<-profmem::profmem({

    res<- run_sim(sim_init = sim,
                  pop_init = Pop,
                  move_cov = moveCov,
                  fleets_init = fleets,
                  hab_init = hab,
                  save_pop_bio = TRUE,
                  survey = NULL, #surv_random, will try to survey after simulation
                  closure = NULL,
                  InParallel = TRUE,
                  nz = nonzero_idx)  #does it runin parallel? Doesnt seem like it
   # })
    end_time <- Sys.time() # record end time
    tot_time <- end_time - start_time # calculate duration of lrren() example

@@

nCoresToUse <- 5

@@

#save results
save.image("/net/home5/blevy/Bens_R_Projects/READ-PDB-blevy2-MFS2/Results/GB_3species_DecPop_IncTemp_RESULTS.RData")
